The \dealii Library, Version 9.6

### 2024-09-13 9.6/paper.tex
Add many TODOs.

\hypersetup{
  pdfauthor={
    Pasquale Claudio Africa,
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Magdalena Schreter-Fleischhacker,
    Jan Philipp Thiele,
    Bruno Turcksin,
    David Wells,
    Vladimir Yushutin
  },
  pdftitle={The deal.II Library, Version 9.6, 2024},
}

@@

\author[7]{Rene~Gassm"{o}ller}
\affil[7]{GEOMAR Helmholtz Centre for Ocean Research Kiel, 24148 Kiel, Germany}

@@

Historically, \trilinos{} has implemented \petra{} objects -- such as
parallel vector, sparsity pattern, and sparse matrix classes -- in its
\epetra{} package that uses \MPI{} as its only source of
parallelism. The \dealii{} interfaces to \trilinos{} are therefore all
built using \epetra{}.
However, several years ago, \trilinos also introduced the
newer \tpetra{} (templated Petra) package that provides additional shared memory 
parallelism and GPU capabilities by building on \kokkos{}. \tpetra{}
is slated to eventually replace \epetra{}, and the latter is indeed
now deprecated. As a consequence, we will eventually have to switch
all of our \trilinos{} interfaces to \tpetra{} and \tpetra{}-based sub-packages.

In the current release, we have put substantial work into this switch.
Since the interface of \tpetra{} was overhauled and modernized 
many of the packages in the third layer now have two generations as well.
Therefore, the \MPI-only set of packages is also referred to as the 
\epetra{} stack and the \MPIx{} packages form the \tpetra{} stack.
As a consequence of the different interfaces, 
a decision was made in the \trilinos{} project to deprecate the \epetra{} stack 
and only provide basic maintenance until a full 
removal from their repository in the course of 2025.

\begin{itemize}
  \item Short overview capabilities of \epetra (MPI parallel, fixed types) [Thiele]
  \item Short overview capabilities of \tpetra (MPI+X via Kokkos, auto diff types, Templated petra) [Thiele]
  \item Current state of the interface (Tpetra based linear algebra, direct solver from Amesos2, preconditioners from Ifpack2) [Thiele \& Kinnewig]
  \item User relevant changes from \epetra: incompatibilities, removed options, changes in the constructor. [Thiele \& Kinnewig]
\end{itemize}

@@

P.C.~Africa was partially supported by the consortium iNEST (Interconnected North-East Innovation Ecosystem),
Piano Nazionale di Ripresa e Resilienza (PNRR) - Missione 4 Componente 2, Investimento 1.5 - D.D. 1058 23/06/2022,
ECS00000043, supported by the European Union's NextGenerationEU program.

@@

W.~Bangerth and T.~Heister were partially
supported by the Computational Infrastructure for Geodynamics initiative
(CIG), through the National Science Foundation (NSF) under Award
No.~EAR-1550901 and EAR-2149126 via The University of California -- Davis.

W.~Bangerth was also partially supported by Awards DMS-1821210 and EAR-1925595.

@@

M.~Fehling was also partially supported by the ERC-CZ grant LL2105
CONTACT funded by the Czech Ministry of Education, Youth and Sports.

@@

@@

D.~Wells was supported by the NSF Award OAC-1931516.

Clemson University is acknowledged for generous allotment of compute time on Palmetto cluster.

@@

\todo[inline]{Update the following to ACCESS, see https://access-ci.org/about/acknowledging-access/}

>>>>

\hypersetup{
  pdfauthor={
    Pasquale Claudio Africa,
    Daniel Arndt,
    Wolfgang Bangerth,
    Bruno Blais,
    Marc Fehling,
    Rene Gassm\"{o}ller,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Magdalena Schreter-Fleischhacker,
    Jan Philipp Thiele,
    Bruno Turcksin,
    David Wells,
    Vladimir Yushutin
  },
  pdftitle={The deal.II Library, Version 9.6, 2024},
}

@@

\author[7]{Rene~Gassm\"{o}ller}
\affil[7]{GEOMAR Helmholtz Centre for Ocean Research Kiel, 24148 Kiel, Germany}

@@

Historically, \trilinos{} has implemented \petra{} objects -- such as
parallel vector, sparsity pattern, and sparse matrix classes -- in its
\epetra{} package that uses \MPI{} as its only source of
parallelism. The \dealii{} interfaces to \trilinos{} are therefore all
built using \epetra{}.
However, several years ago, \trilinos also introduced the
newer \tpetra{} (``templated'' Petra) package that provides additional shared memory 
parallelism and GPU capabilities by building on \kokkos{}. \tpetra{}
is slated to eventually replace \epetra{}, and the latter is indeed
now deprecated with removal slated for 2025. As a consequence, we will
eventually have to switch all of our \trilinos{} interfaces to
\tpetra{}; the same is true for the need to switch to \tpetra{}-based
sub-packages replacing existing \trilinos sub-packages (for example,
Ifpack2 instead of Ifpack).

In the current release, we have put substantial work into this switch.

\todo[inline]{Sebastian \& Jan Philipp: Please complete}

\begin{itemize}
  \item Short overview capabilities of \epetra (MPI parallel, fixed types) [Thiele]
  \item Short overview capabilities of \tpetra (MPI+X via Kokkos, auto diff types, Templated petra) [Thiele]
    \todo[inline]{Keep discussion of the two items above as short as
      you can -- we're describing the changes in deal.II, not some
      other package. Perhaps roll what you want to say into the
      paragraphs above?}
  \item Current state of the interface (Tpetra based linear algebra, direct solver from Amesos2, preconditioners from Ifpack2) [Thiele \& Kinnewig]
  \item User relevant changes from \epetra: incompatibilities, removed
    options, changes in the constructor. [Thiele \& Kinnewig]
    \todo[inline]{These last two items are the important ones.}
\end{itemize}

@@

P.~C.~Africa was partially supported by the consortium iNEST (Interconnected North-East Innovation Ecosystem),
Piano Nazionale di Ripresa e Resilienza (PNRR) - Missione 4 Componente 2, Investimento 1.5 - D.D. 1058 23/06/2022,
ECS00000043, supported by the European Union's NextGenerationEU program.

@@

W.~Bangerth and T.~Heister were partially
supported by the Computational Infrastructure for Geodynamics initiative
(CIG), through the National Science Foundation (NSF) under Award
No.~EAR-2149126 via The University of California -- Davis.

W.~Bangerth was also partially supported by Award EAR-1925595.

@@

M.~Fehling was also partially supported by the ERC-CZ grant LL2105
CONTACT, funded by the Czech Ministry of Education, Youth and Sports.

\todo[inline]{Rene: anything to list here?}

@@

\todo[inline]{Sebastian: Anything to list here?}

@@

\todo[inline]{Jan Philipp: Anything to list here?}

D.~Wells was supported by NSF Award OAC-1931516.

Clemson University is acknowledged for generous allotment of compute
time on the Palmetto cluster.

\todo[inline]{Did anyone actually use TACC resources? Timo or Marc? If
not, we need to delete the following sentence.}

@@

\todo[inline]{Marc: Update the following to ACCESS, see https://access-ci.org/about/acknowledging-access/}
